Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
proof of prop4 is word-y now.

\begin{figure*}[tb]
    \centering
    \includegraphics*{gen-graph-runtimes.pdf}
    \caption{In the first two plots, the cumulative number of instances solved over time, for the
        induced and non-induced problems, with different values of $k$. We also show the results of
        iteratively increasing $k$ until a solution is found, and in the induced case, the
        performance of two leading maximum common subgraph algorithms. In the third plot, results
        comparing our algorithm with iteratively increasing $k$ to other approaches on maximum
        common induced subgraph instances.}\label{figure:runtimes}
\end{figure*}

>>>>

\begin{figure*}[tb]
    \centering
    \includegraphics*{gen-graph-runtimes.pdf}
    \caption{In the first two plots, the cumulative number of instances solved over time, for the
        induced and non-induced problems, with different values of $k$. We also show the results of
        iteratively decreasing $k$ until a solution is found, and in the induced case, the
        performance of two leading maximum common subgraph algorithms. In the third plot, results
        comparing our algorithm with iteratively decreasing $k$ to other approaches on maximum
        common induced subgraph instances.}\label{figure:runtimes}
\end{figure*}
